`phyr`: An R package for model-based phylogenetic analyses

### 2018-11-02 ms.Rmd
add main function table [skip ci]

```{r knitr_options, include = FALSE}
if(!require("xfun")) devtools::install_github("yihui/xfun")
if(!require("phyr")) devtools::install_github("daijiang/phyr")
xfun::pkg_attach2(c("knitr", "kableExtra", "dplyr"))
# opts_knit$set(root.dir = normalizePath("../"))
opts_chunk$set(fig.align='center', cache = FALSE, warning = FALSE, 
               message = FALSE, echo = TRUE)
options(digits = 3, width = 88)
```

@@

A table with all main functions

>>>>

```{r knitr_options, include = FALSE}
if(!require("xfun")) devtools::install_github("yihui/xfun")
if(!require("phyr")) devtools::install_github("daijiang/phyr")
xfun::pkg_attach2(c("knitr", "kableExtra", "kableExtra", "dplyr"))
# opts_knit$set(root.dir = normalizePath("../"))
opts_chunk$set(fig.align='center', cache = FALSE, warning = FALSE, 
               message = FALSE, echo = TRUE)
options(digits = 3, width = 88, knitr.kable.NA = '')
```

@@

Main functions provided by `phyr` can be found in Table \@ref(tab:mainFunc).

(ref:maunFuncCaption) Main functions in `phyr`.

```{r mainFunc, echo=FALSE}
read.csv("phyr_func.csv", check.names = FALSE) %>% 
  knitr::kable(caption = "(ref:maunFuncCaption)", booktab = T) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "scale_down", "hover"),
                latex_options = c("striped")) %>% 
  kableExtra::column_spec(1, width = "20%")
```
